\documentclass[UTF8,4pt,a3paper,space]{article}
\usepackage{geometry}
\geometry{landscape}
\usepackage{setspace}
\setstretch{0.5}
\usepackage[UTF8]{ctex}
\usepackage{multicol}
\geometry{top = 0cm, bottom = 1.5cm, left = 1cm, right = 0.5cm}
\begin{document}
\begin{multicols}{4}
\section{daltonism$^8$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 【医】色盲(=color blindness)}\begin{itemize}
\itemsep-0.5em
    \item The artist's daltonism made it difficult for him to accurately depict the colors in his paintings. 
\end{itemize}
\hrulefill


\section{orthopedics$^7$}
\subsubsection*{\ \ \ \ 【医】整形外科, 整形术}\begin{itemize}
\itemsep-0.5em
    \item If this description matches your behavior, you're probably a weekend warrior, said Jeffrey Spang, MD, an assistant professor of orthopedics at the University of North Carolina School of Medicine.    \item The doctor specialized in orthopedics and was able to diagnose the patient's condition with ease. 
\end{itemize}
\hrulefill


\section{sceptre$^5$}
\subsubsection*{\ \ \ \ 笏, 节杖, 王权(=scepter)}\begin{itemize}
\itemsep-0.5em
    \item Therefore, let me go, for I must wander again over the world, and may not tarry here, though ye bring me the crown and the sceptre.    \item The wizard held the sceptre aloft, its glowing tip illuminating the darkened chamber. 
\end{itemize}
\hrulefill


\section{pericope$^8$}
\subsubsection*{\ \ \ \ (从书中选出的)章节, 选段}\begin{itemize}
\itemsep-0.5em
    \item You're going to pay really good attention to all the details of the pericope.    \item You want to concentrate on the details of your pericope to try to find out what the message is.    \item The pastor's pericope on forgiveness resonated deeply with the congregation. 
\end{itemize}
\hrulefill


\section{sphinx$^7$}
\subsubsection*{\ \ \ \ 【希神】斯芬克斯(有翼的狮身女怪, 传说她常叫过路行人猜谜, 猜不出者即遭杀害)}\begin{itemize}
\itemsep-0.5em
    \item The sphinx sat at the edge of the desert, its enigmatic gaze piercing through the sandy dunes. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item the great sphinx\ \ （古埃及）狮身人面像
\end{itemize}
\hrulefill


\section{paysage$^5$}
\subsubsection*{\ \ \ \ 【法】乡村景色}\begin{itemize}
\itemsep-0.5em
    \item The painter spent hours admiring the paysage from the hilltop, capturing its rolling hills and sparkling streams in his canvas. 
\end{itemize}
\hrulefill


\section{morphemics$^8$}
\subsubsection*{\ \ \ \ 【用作单】【语】语素学,词素学}\begin{itemize}
\itemsep-0.5em
    \item The linguist studied morphemics to better understand the structure of language. 
\end{itemize}
\hrulefill


\section{covin$^6$}
\subsubsection*{\ \ \ \ ［古］欺诈}\begin{itemize}
\itemsep-0.5em
    \item The detective was covin in his theory that the murderer was hiding in plain sight. 
\end{itemize}
\hrulefill


\section{superfuse$^7$}
\subsubsection*{\ \ \ \ 【罕】倾注, 浇盖}\begin{itemize}
\itemsep-0.5em
    \item The new superfuse in the hospital was able to handle twice as many patients as the old one. 
\end{itemize}
\hrulefill


\section{tar$^4$}
\subsubsection*{\ \ \ \ 煤油；焦油}\begin{itemize}
\itemsep-0.5em
    \item The sailor carefully tarred the boat to protect it from the elements. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item coal tar   \item tar pitch   \item coal tar pitch   \item coke tar   \item pine tar\end{itemize}
\hrulefill


\end{multicols}
\end{document}
