\documentclass[UTF8,4pt,a3paper,space]{article}
\usepackage{geometry}
\geometry{landscape}
\usepackage{setspace}
\setstretch{0.5}
\usepackage[UTF8]{ctex}
\usepackage{multicol}
\geometry{top = 0cm, bottom = 1.5cm, left = 1cm, right = 0.5cm}
\begin{document}
\begin{multicols}{4}
\section{sensible$^5$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 可感觉的；明智的}\begin{itemize}
\itemsep-0.5em
    \item She seems very sensible.    \item sensible advice    \item It’s sensible to keep a note of your passport number.    \item Moving house seemed like the sensible thing to do .    \item  He wore sensible shoes for his hiking trip to avoid blisters. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item sensible heat   \item sensible of\end{itemize}
\hrulefill


\section{sign$^4$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 记号；标志；征兆}\begin{itemize}
\itemsep-0.5em
    \item A paw print in the dust was a sign that a tiger was close.    \item There were no signs of forced entry into the house.    \item The sign on the store window read "Open Until 9 PM". 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item sign up   \item sign on   \item sign for   \item sign in   \item sign up for\end{itemize}
\hrulefill



\section{explicit$^7$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 清楚的，明确的}\begin{itemize}
\itemsep-0.5em
    \item The contrast could not have been made more explicit.    \item explicit knowledge of grammar    \item The kidnappers gave us explicit instructions not to involve the police.    \item Be explicit when you talk about money with your family.    \item The teacher made it clear that she expected no explicit content in the student's essay. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item explicit expression\ \ 显式表达式
   \item explicit knowledge\ \ 显性知识；外显知识
   \item explicit memory\ \ 外显记忆
   \item explicit function\ \ 显函数
   \item explicit formulation\ \ 显式
\end{itemize}
\hrulefill


\section{wreck$^6$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 破坏，船舶失事；失事船只}\begin{itemize}
\itemsep-0.5em
    \item He was still alive when they pulled him from the wreck.    \item He was left to pick up the wreck of his car after the accident. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item train wreck\end{itemize}
\hrulefill


\section{ravage$^6$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 毁坏，蹂躏；抢劫，掠夺}\begin{itemize}
\itemsep-0.5em
    \item a country ravaged by civil war    \item His health was gradually ravaged by drink and drugs.    \item The storm ravaged the coastal town, leaving behind a trail of destruction and devastation. 
\end{itemize}
\hrulefill


\section{wreathe$^6$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 覆盖，包围}\begin{itemize}
\itemsep-0.5em
    \item The ship was wreathed in smoke.    \item Fog wreathes the temples.    \item She wreathed her hair with flowers to match her dress. 
\end{itemize}
\hrulefill


\section{impede$^7$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 妨碍；阻碍}\begin{itemize}
\itemsep-0.5em
    \item Storms at sea impeded our progress.    \item The traffic police officer's radar gun impeded the speeding car's getaway. 
\end{itemize}
\hrulefill


\section{thesis$^7$}
\subsubsection*{\ \ \ \ \ \ \ \ \ (学位)论文}\begin{itemize}
\itemsep-0.5em
    \item Cynthia’s still working on her thesis.    \item She spent hours working on her thesis, pouring over research and data to ensure its accuracy. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item graduation thesis\ \ 毕业论文；毕业设计
   \item thesis writing\ \ 论文写作
   \item scientific thesis\ \ 科学论点
   \item thesis defense\ \ 论文答辩
\end{itemize}
\hrulefill


\section{precedent$^7$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 先例，前例}\begin{itemize}
\itemsep-0.5em
    \item a legal precedent    \item The company's decision was based on a precedent set by their competitors. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item judicial precedent\ \ 司法判例
   \item condition precedent\ \ 先决条件
   \item conditions precedent\ \ 先决条件
\end{itemize}
\hrulefill


\section{lofty$^6$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 极高的，高尚的，高傲的}\begin{itemize}
\itemsep-0.5em
    \item He stayed at the Four Seasons Hotel, from whose lofty heights he could see across New York.    \item The ambitious goal of launching a space station seemed lofty to many skeptics. 
\end{itemize}
\hrulefill


\section{fridge$^5$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 冰箱}\begin{itemize}
\itemsep-0.5em
    \item Then all three of you sign the contract and post in on the fridge.    \item I want this beer to chill so I'll leave it in the fridge for an hour.    \item It can be anything: spoiled milk from the back of your fridge right down to tar and feathers.    \item The family stored their groceries in the cramped fridge until they could find a larger one. 
\end{itemize}
\hrulefill


\section{immune$^6$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 免除的；安全的，不受影响的}\begin{itemize}
\itemsep-0.5em
    \item Once we’ve had the disease, we’re immune for life.    \item The baby was immune to the virus and didn't get sick. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item immune system   \item immune response   \item acquired immune deficiency syndrome   \item immune globulin   \item immune surveillance   \item immune complex\end{itemize}
\hrulefill


\section{scratch$^4$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 抓；搔，挖}\begin{itemize}
\itemsep-0.5em
    \item John yawned and scratched his leg.    \item Try not to scratch.    \item She scratched her head in confusion. 
\end{itemize}
\begin{itemize}
\itemsep-0.5em
   \item from scratch   \item start from scratch   \item up to scratch   \item without a scratch   \item scratch the surface\end{itemize}
\hrulefill


\section{circulate$^6$}
\subsubsection*{\ \ \ \ \ \ \ \ \ 循环，流通}\begin{itemize}
\itemsep-0.5em
    \item Swimming helps to get the blood circulating through the muscles.    \item Ceiling fans circulated warm air around the room.    \item The new idea circulated quickly through the team. 
\end{itemize}
\hrulefill


\end{multicols}
\end{document}
